Software Citation Principles

### 2016-03-02 sc-principles/software-citation-principles.tex
adding additional sentence in principle 1
Updates from ShareLaTeX

The Force11 Software Citation Working Group~\cite{f11scwg} was created in April 2015.
It gathered members (see Appendix~\ref{app:wg_members}), and then in June 2015 began studying this, with a number of meetings
and some off-line work by group members to gather materials documenting existing
practices in member disciplines; gather materials from workshops and other reports;
review those materials, identifying overlaps and differences; and draft this resulting document,
which will be presented and discussed at the Force2016 Conference \cite{force2016}
in April 2016.  We expect that
this discussion may lead to a second, final version, and we also
plan to have a follow-on working group that will work with stakeholders to ensure that
these principles impact the scientific process.

@@

\rowcolors{5}{white}{gray!25}
\begin{table}[htbp]
\caption{Use cases for software citation, adapted from \cite{SC-Use-Cases} \flnote{Also, I noticed that some entries have the same requirements: maybe they could be combined to one line?} \dmnote{I would leve them separate. What about adding a column for license?}}
\centering
\scriptsize\setlength{\tabcolsep}{2.5pt}
\begin{tabular}{@{}l l c c c c c c c c@{}}
\toprule
 & & \multicolumn{6}{c}{Requirements} \\
 \cmidrule{3-10}
\multirow{2}{*}{Stakeholder} &	\multirow{2}{*}{Use\slash wants to} 	 &  Software  & \multirow{2}{*}{Author(s)} & \multirow{2}{*}{Version \#} & Release & Location\slash  & \multirow{2}{*}{UID} & Indexed & \multirow{2}{*}{Role} \\
& & name &  &  &  date & repository &  & citations & \\
\midrule
Researcher            & use someone else's software for a paper      & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             &             \\
Researcher            & use someone else's software for new software & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             &             \\
Researcher            & contribute to software                   & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             & \textbullet \\
Researcher            & find citations of software               & \textbullet &             &             &             &             & \textbullet & \textbullet &             \\
Researcher            & get credit for software development          & \textbullet & \textbullet &             & \textbullet & \textbullet & \textbullet &             & \textbullet \\
Researcher            & ``reproduce'' analysis                   & \textbullet &             & \textbullet & \textbullet & \textbullet & \textbullet &             &             \\
Researcher            & benchmark software                       & \textbullet &             & \textbullet & \textbullet & \textbullet & \textbullet &             &             \\
Researcher            & find software to implement task          & \textbullet & \textbullet &             &             & \textbullet & \textbullet & \textbullet &             \\
Publisher             & publish software paper                   & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             &             \\
Publisher             & publish papers that cite software        & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             \\
Indexer               & build catalog of software                & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             \\
Domain group          & build catalog of software                & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             &             \\
Library\slash archive & build catalog of software                & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             &             \\
Repository            & show scientific impact of holdings       & \textbullet &             &             &             &             & \textbullet & \textbullet &             \\
Funder                & show how funded software has been used   & \textbullet &             &             &             &             & \textbullet & \textbullet &             \\
\bottomrule
\end{tabular}
\label{tab:use_cases}
\end{table}%

@@

\appendix

\section{Working Group Membership}
\label{app:wg_members}

\katznote{should make affiliation styles more consistent}

\katznote{should check to make sure these are all still right, such as for me and Bill Mills}

Alberto Accomazzi, Harvard-Smithsonian CfA

Alice Allen, Astrophysics Source Code Library

Carl Boettiger, UC Berkeley

Sou-Cheng Choi , NORC at the University of Chicago \& Illinois Institute of Technology

Neil Chue Hong, Software Sustainability Institute

Tom Crick, Cardiff Metropolitan University

Martin Fenner, Public Library of Science

Merc\`e Crosas, IQSS, Harvard University

Christopher Erdmann, Harvard-Smithsonian CfA

Ian Gent, University of St Andrews, recomputation.org

Paul Groth, Elsevier Labs

Melissa Haendel, OHSU

Stephanie Hagstrom, Force11

Robert Hanisch, NIST/ODI

Edwin Henneken, Harvard-Smithsonian CfA

Ivan Herman, W3C

James Howison, UTexas

Lorraine Hwang, UC Davis

Thomas Ingraham, F1000Research

Matthew B. Jones, NCEAS, UC Santa Barbara

Catherine Jones, Science and Technology Facilities Council

Daniel S. Katz, U Chicago \& Argonne Natl Lab (co-chair)

Alexander Konovalov, University of St Andrews

John Kratz, California Digital Library

Jennifer Lin, Public Library of Science

Frank L\"offler, Louisiana State University

Brian Matthews, Science and Technology Facilites Council

Abigail Cabunoc Mayes, Mozilla Science Lab

Daniel Mietchen, NIH

Bill Mills, Mozilla Science Lab

Evan Misshula, CUNY Graduate Center

August Muench, American Astronomical Society

Fiona Murphy, Independent Researcher

Lars Holm Nielsen, CERN

Kyle Niemeyer, Oregon State University

Karthik Ram, University of California, Berkeley

Fernando Rios, Johns Hopkins University

Ashley Sands, UCLA Information Studies

Soren Scott , Independent Researcher

Frank J. Seinstra, Netherlands eScience Center

Arfon Smith, GitHub (co-chair)

Kaitlin Thaney, Mozilla Science Lab

Ilian Todorov, STFC

Matt Turk, University of Illinois

Miguel de Val-Borro, Princeton University

Daan Van Hauwermeiren, Ghent University

Stijn Van Hoey, Ghent University

Belinda Weaver, The University of Queensland

Nic Weber, University of Washington iSchool

>>>>

The Force11 Software Citation Working Group~\cite{f11scwg} was created in April 2015.
It gathered members, and then in June 2015 began studying this, with a number of meetings
and some off-line work by group members to gather materials documenting existing
practices in member disciplines; gather materials from workshops and other reports;
review those materials, identifying overlaps and differences; and draft this resulting document,
which will be presented and discussed at the Force2016 Conference \cite{force2016}
in April 2016.  We expect that
this discussion may lead to a second, final version, and we also
plan to have a follow-on working group that will work with stakeholders to ensure that
these principles impact the scientific process.

@@

\rowcolors{5}{white}{gray!25}
\begin{table}[htbp]
\caption{Use cases for software citation, adapted from \cite{SC-Use-Cases} \flnote{Also, I noticed that some entries have the same requirements: maybe they could be combined to one line?} \dmnote{I would leave them separate. What about adding a column for license?}}
\centering
\scriptsize\setlength{\tabcolsep}{2.5pt}
\begin{tabular}{@{}l l c c c c c c c c@{}}
\toprule
 & & \multicolumn{6}{c}{Requirements} \\
 \cmidrule{3-10}
\multirow{2}{*}{Stakeholder} &	\multirow{2}{*}{Use\slash wants to \dmnote{should start with a verb}} 	 &  Software  & \multirow{2}{*}{Author(s)} & \multirow{2}{*}{Version \#} & Release & Location\slash  & \multirow{2}{*}{UID} & Indexed & \multirow{2}{*}{Role} \\
& & name &  &  &  date & repository &  & citations & \\
\midrule
Researcher            & someone else's software for a paper      & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             &             \\
Researcher            & someone else's software for new software & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             &             \\
Researcher            & contribute to software                   & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             & \textbullet \\
Researcher            & find citations of software               & \textbullet &             &             &             &             & \textbullet & \textbullet &             \\
Researcher            & credit for software development          & \textbullet & \textbullet &             & \textbullet & \textbullet & \textbullet &             & \textbullet \\
Researcher            & ``reproduce'' analysis                   & \textbullet &             & \textbullet & \textbullet & \textbullet & \textbullet &             &             \\
Researcher            & benchmark software                       & \textbullet &             & \textbullet & \textbullet & \textbullet & \textbullet &             &             \\
Researcher            & find software to implement task          & \textbullet & \textbullet &             &             & \textbullet & \textbullet & \textbullet &             \\
Publisher             & publish software paper                   & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             &             \\
Publisher             & publish papers that cite software        & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             \\
Indexer               & build catalog of software                & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             \\
Domain group          & build catalog of software                & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             &             \\
Library\slash archive & build catalog of software                & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             &             \\
Repository            & show scientific impact of holdings       & \textbullet &             &             &             &             & \textbullet & \textbullet &             \\
Funder                & show how funded software has been used   & \textbullet &             &             &             &             & \textbullet & \textbullet &             \\
\bottomrule
\end{tabular}
\label{tab:use_cases}
\end{table}%

@@
